Almost compatible functions and infinite length games

### 2015-11-17 articles/almost-compatible-functions-and-topological-games/article.tex
introduction to s'kappa paper

\section{Almost compatible functions}

>>>>

\section{Introduction}

  \begin{definition}
    Two functions \(f,g\) are almost compatible, that is, \(f\sim g\) when
    \(\{a\in\dom f\cap\dom g:f(a)\not=g(a)\}\) is finite.
  \end{definition}

  Marion Scheepers used almost compatible functions in \cite{MR1129143} in order
  to study the existence of limited information strategies on a variation
  of the meager-nowhere dense game he introduced in \cite{MR1183703}.

  \begin{game}
    Let \(\schFillStrictGame\kappa\) denote
    \term{Scheepers' strict countable-finite union game}
    with two players \(\pl C\), \(\pl F\). In round \(0\), \(\pl C\) chooses
    \(C_0\in[\kappa]^{\leq\omega}\), followed by \(\pl F\) choosing
    \(F_0\in[\kappa]^{<\omega}\). In round \(n+1\), \(\pl C\) chooses
    \(C_{n+1}\in[\kappa]^{\leq\omega}\) such that \(C_{n+1}\supset C_n\), followed
    by \(\pl F\) choosing \(F_{n+1}\in[\kappa]^{<\omega}\).

    \(\pl F\) wins the game if
    \(\bigcup_{n<\omega} F_n\supseteq\bigcup_{n<\omega} C_n\); otherwise,
    \(\pl C\) wins.
  \end{game}

  Of course, with perfect information this game is trivial: during round
  \(n\) player \(\pl F\) simply chooses \(n\) ordinals from each of the
  \(n\) countable sets played by \(\pl C\). However, if \(\pl F\) is limited
  to using information from the last \(k\) moves by \(\pl C\) during each
  round, the task becomes more difficult. Call such a strategy a
  \term{\(k\)-tactical strategy} or \term{\(k\)-tactic}; if using the round
  number is allowed, then the strategy is called a \term{\(k\)-Markov strategy}
  or a \term{\(k\)-mark}.

  \begin{definition}
    The statement \(S(\kappa)\) (given as \(S(\kappa,\aleph_0,\omega)\)
    in \cite{MR1129143}) claims that there exist injections
    \(f_A:A\to\omega\) for each \(A\in[\kappa]^{\leq\aleph_0}\) such that
    the collection \(\{f_A:A\in[\kappa]^{\leq\aleph_0}\}\) is pairwise
    almost compatible.
  \end{definition}

  In the same paper, Scheepers noted that \(S(\omega_1)\) holds in \(ZFC\),
  and that it's possible to force \(\mf c\) to be arbitrarily large
  while preserving \(S(\mf c)\). However, \(S(\mf c^+)\) always fails.
  This axiom may be applied to obtain a winning \(2\)-tactic for \(\pl F\)
  in the countable-finite game.

  In \cite{clontzMengerGamePreprint}, Clontz related this game to a game
  which may be used to characterize the Menger covering property of a
  topological space.

  \begin{game}
    Let \(\menGame{X}\) denote the \term{Menger game} with players \(\pl C\),
    \(\pl F\).
    In round \(n\), \(\pl C\) chooses an open cover \(\mc U_n\), followed by
    \(\pl F\)
    choosing subset \(F_n\) of \(X\) which may be finitely covered by \(\mc U_n\).

    \(\pl F\) wins the game if \(X = \bigcup_{n<\omega}F_n\),
    and \(\pl C\) wins otherwise.
  \end{game}

  This characterization is slightly different than the typical characterization
  in which the second player first chooses a specific
  finite subcollection \(\mc F_n\) of the cover itself and lets
  \(F_n=\bigcup \mc F_n\), denoted as \(G_{fin}(\mc O,\mc O)\)
  in \cite{MR1378387}.
  However, it's easily seen that these games are equivalent
  for perfect information strategies (so both characterize
  the Menger property), and this characterization is
  more convenient for our concerns.

  \begin{definition}
    Let \(\oneptlind\kappa=\kappa\cup\{\infty\}\) where \(\kappa\) is
    discrete and \(\infty\)'s neighborhoods are the co-countable sets
    containing it.
  \end{definition}

  The relationship between \(\schFillStrictGame\kappa\) and
  \(\menGame{\oneptlind\kappa}\) is strong; in both games \(\pl C\) essentially
  chooses a countable subset of \(\kappa\) followed by \(\pl F\) choosing
  a finite subset of that choice, and it's easy to see the winning perfect
  information strategy for \(\pl F\) in both games.
  In addition, it was shown in
  \cite{clontzMengerGamePreprint} that when \(S(\kappa)\) holds,
  \(\pl F\) has a winning \(2\)-Markov strategy in
  \(\menGame{\oneptlind\kappa}\).

  One source of motivation is to make progress on the following open question:

  \begin{question}
    Does there exist a topological space \(X\) for which
    \(\pl F\win\menGame{X}\) but \(\pl F\notkmarkwin{2}\menGame{X}\)?
    (That is, the second player can win the Menger game on \(X\)
    with perfect information but not with \(2\)-Markov information.)
  \end{question}

  One might hope that \(\oneptlind{(\mf c^+)}\) might answer this question
  in the affirmative as \(S(\mf c^+)\) fails, but we will show that assuming
  \(V=L\), \(\pl F\kmarkwin{2}\menGame{\oneptlind\kappa}\) for all
  cardinals \(\kappa\).

  \section{One-to-one and finite-to-one almost compatible functions}

  We may weaken Scheeper's \(S(\kappa)\) as follows:
